\\fontsize{12pt}{3pt}\\selectfont \\textbf{\\textit{Journal: Ecosphere. Manuscript ID: ECS23-0342. Manuscript type: Article}}

### 2024-02-13 manuscript/manuscriptRW.Rmd
correct the open research statement

date: $^1$ETH Zurich. Department of Environmental Systems Science. Institute of Terrestrial Ecosystems. Universitätstrasse 16, 8092 Zürich, Switzerland. \newline

@@

**OPEN RESEARCH STATEMENT:** This submission uses novel code, both the
data and code are provided in an external repository to be evaluated
during the peer review process. The repository can be downloaded from
[this figshare private link:
https://figshare.com/s/100857ba67d2351dcb15](https://figshare.com/s/100857ba67d2351dcb15).
The protocol is available at @díaz-yáñez2022 ([with link:
https://osf.io/czdxp/](https://osf.io/czdxp/)). We will make publicly
available the code and data if the manuscript is accepted.

>>>>

date: $^1$ETH Zurich. Department of Environmental Systems Science. Institute of Terrestrial Ecosystems. Forest Ecology. Universitätstrasse 16, 8092 Zürich, Switzerland. \newline

@@

**OPEN RESEARCH STATEMENT:** This paper uses novel protocol, data and
code, alle are available open access. The protocol and the protocol data
is available at @díaz-yáñez2022. The data is available at
@diaz-yanez2023. The repository containing the code used in the
analysis, figure creation and manuscript writing can be downloaded from
XXXXXXX.
